$p$-adic precision

### 2014-02-12 padicprec.tex
typos

\begin{deftn}\label{deftn:analyticNP}
Let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ be locally analytic map $E \rightarrow F$.  Let $x \in E$, and let $f(x+h)=f(x)+\sum_{k \geq 0}^{+\infty} L_k \cdot (h,\dots,h)$ be the power series development of $f$ at $x$.
Let $F(t) = \sum_{k\geq 0}^{+\infty} \interleave L^{k+1}(x) \interleave  t^k \in \mathbb{R}[[t]].$

We define $NP(f,x)$ to be the function defined by its Newton polygon, the lower convex hull of the $(k,\log ( \interleave L^{k+1}(x) \interleave)),$ with $k \geq 0.$
\end{deftn}

We now prove that the knowledge of $NP(f,x)$ is enough to recover $\delta$.

\begin{prop}\label{prop:locanalytic}
Let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ and the $L_k$'s be as in definition \ref{deftn:analyticNP}. We assume $L_1$ is surjective. 
Let $C$ be given by the Banach-Schauder theorem for $L_1$, $\varepsilon = \frac{1}{C}$. 
Let $\mu$ be the slope of the line passing by $(0, \log_p \varepsilon)$ and tangent to $NP(f,x)$.
Then $r$ such that $\mu=\log_p r$ is enough for lemma \ref{lem:main}.
\end{prop}
\begin{proof}
Let us assume that $x=0$, $f(0)=0$, and for $r>0$, $f(x)=L_1 \cdot x +\sum_{n \geq 2} L_n \cdot (x, \dots,x)$ is the Taylor serie expansion of $f$ at $0$, coinciding on $B_E (0,r)$.

@@

Recall that any 
ideal $I \subset K[\XX]$ admits a unique reduced Gr\"obner basis. We can 
then consider the application mapping a family $(f_1, \ldots, f_s)$ of 
\emph{homogeneous}\footnote{This restriction will be convenient for us 
mainly because we are using the article \cite{Vaccon}, which deals only 
with homogeneous polynomials. It is however probably not essential.} 
polynomials of fixed degrees to the reduced Gr\"obner basis $(g_1, 
\ldots, g_t)$. It follows from Theorem 1.1 of \cite{Vaccon} that this 
application at $(f_1, \ldots, f_s)$ is continuous provided that:
\begin{itemize}
\item the sequence $(f_1, \ldots, f_s)$ is regular
\item for all $i \in \{1, \ldots, s\}$, the ideal generated by
$f_1, \ldots, f_i$ is wearly-$w$ where $w$ denotes the fixed monomial
order (\emph{cf} \cite{Vaccon} for more precisions).
\end{itemize}
A similar argument proves that it is actually differentiable at such
points. We are now going to compute the differential. For this we
remark that since the families $(f_1, \ldots, f_s)$ and $(g_1, \ldots,
g_t)$ generate the same ideal, we have a relation:
\begin{equation}
\label{eq:prodgrobner}
(g_1, \ldots, g_t) = (f_1, \ldots, f_s) \cdot A
\end{equation}
where $A$ is a $(s \times t)$ matrix with coefficients in $K[\XX]$.
Moreover following Vaccon's construction, we see that the entries of $A$ 
can be chosen in such a way that they define differentiable functions.
Differentiating Eq.~\eqref{eq:prodgrobner}, we get:
$$(d g_1, \ldots, d g_t) =
(d f_1, \ldots, d f_s) \cdot A + (f_1, \ldots, f_s) \cdot dA.$$
Finally, using that we are working with \emph{reduced} Gr\"obner
basis, the above equality implies that $d g_i$ is the remainder in
the division of the $i$-th coefficient of the product
$(d f_1, \ldots, d f_s) \cdot A$ by the family $(g_1, \ldots, g_t)$.

@@

Let us first compute the differential of the function $\det : M_n(K) \to 
K$. It is a standard computation. To begin with, we consider an 
invertible matrix $M$ and write:
\begin{eqnarray*}
\det(M + dM) &=& \det(M) \cdot \det(I + M^{-1} \cdot dM)  \\
&=& \det(M) \cdot \big(1 + \tr(M^{-1} \cdot dM)\big) \\
&=& \det(M) + \tr(\com(M) \cdot dM)
\end{eqnarray*}
where $\com(M)$ denotes the comatrix of $M$. The differential of 
$\det$ at $M$ is then $dM \mapsto \tr(\com(M) \cdot dM)$. It turns
out that this formula is still valid when $M$ is not invertible.
The same computation extends readily to characteristic polynomials,
since they are defined as determinants. More precisely, let us 
consider the function $\chi : M_n(K) \to K_{\leq n}[X]$ (where
the latter ring denotes the finite dimensional vector space of 
polynomials over $K$ of degree at most $n$) taking a matrix $M$
to its characteristic polynomial $\det(X-M)$.
Then $\chi$ is differentiable at each point $M \in M_n(K)$ and its 
differential is given by $dM \mapsto \tr(\com(X{-}M) \cdot dM)$.

>>>>

\begin{prop}\label{prop:locanalytic}
Let $E$ and $F$ be two complete normed $K$-vector spaces, and let $f$ be locally analytic map $E \rightarrow F$.  Let $x \in E$, and let $f(x+h)=f(x)+\sum_{k \geq 0}^{+\infty} L_k \cdot (h,\dots,h)$ be the power series development of $f$ at $x$. We assume $L_1$ is surjective. 
Let $C$ be given by the Banach-Schauder theorem for $L_1$, $\varepsilon = \frac{1}{C}$. 
Let $F(t) = \sum_{k\geq 0}^{+\infty} \interleave L^{k+1}(0) \interleave  t^k \in \mathbb{R}[[t]]$, let $NP_F$ be its Newton polygon.
Let $\mu$ be the slope of the line passing by $(0, \log_p \varepsilon)$ and tangent to $NP_F$.
Then $r$ such that $\mu=\log_p r$ is enough for lemma \ref{lem:main}.
\end{prop}
\begin{proof}
Let us assume that $x=0$, $f(0)=0$, and for $r>0$, $f(x)=L_1 \cdot x +\sum_{n \geq 2} L_n \cdot (x, \dots,x)$ is the Taylor serie expansion of $f$ at $0$, coinciding on $B_E (0,r)$.

@@

Recall that any 
ideal $I \subset K[\XX]$ admits a unique reduced Gr\"obner basis. We can 
then consider the application mapping a family $(f_1, \ldots, f_s)$ of 
\emph{homogeneous}\footnote{This restriction will be convenient for us 
mainly because we are using the article \cite{Vaccon}, which deals only 
with homogeneous polynomials. It is however probably not essential.} 
polynomials of fixed degrees to the reduced Gr\"obner basis $(g_1, 
\ldots, g_t)$. It follows from Theorem 1.1 of \cite{Vaccon} that this 
application is continuous at $(f_1, \ldots, f_s)$ provided that:
\begin{itemize}
\item the sequence $(f_1, \ldots, f_s)$ is regular
\item for all $i \in \{1, \ldots, s\}$, the ideal generated by
$f_1, \ldots, f_i$ is wearly-$w$ where $w$ denotes the fixed monomial
order (\emph{cf} \cite{Vaccon} for more precisions).
\end{itemize}
A similar argument proves that it is actually differentiable at such
points. We are now going to compute the differential. For this we
remark that since the families $(f_1, \ldots, f_s)$ and $(g_1, \ldots,
g_t)$ generate the same ideal, we have a relation:
\begin{equation}
\label{eq:prodgrobner}
(g_1, \ldots, g_t) = (f_1, \ldots, f_s) \cdot A
\end{equation}
where $A$ is a $(s \times t)$ matrix with coefficients in $K[\XX]$.
Moreover following Vaccon's construction, we see that the entries of $A$ 
can be chosen in such a way that they define differentiable functions.
Differentiating Eq.~\eqref{eq:prodgrobner}, we get:
$$(d g_1, \ldots, d g_t) =
(d f_1, \ldots, d f_s) \cdot A + (f_1, \ldots, f_s) \cdot dA.$$
Finally, using that we are working with \emph{reduced} Gr\"obner
basis, the above equality implies that $d g_i$ is the remainder in
the division of the $i$-th coefficient of the product
$(d f_1, \ldots, d f_s) \cdot A$ by the family $(g_1, \ldots, g_t)$.

@@

Let us first compute the differential of the function $\det : M_n(K) \to 
K$. It is a standard computation. To begin with, we consider an 
invertible matrix $M$ and write:
\begin{eqnarray*}
\det(M + dM) &=& \det(M) \cdot \det(I + M^{-1} \cdot dM)  \\
&=& \det(M) \cdot \big(1 + \tr(M^{-1} \cdot dM)\big) \\
&=& \det(M) + \tr(\com(M) \cdot dM)
\end{eqnarray*}
where $\com(M)$ denotes the comatrix of $M$. The differential of 
$\det$ at $M$ is then $dM \mapsto \tr(\com(M) \cdot dM)$. It turns
out that this formula is still valid when $M$ is not invertible.
The same computation extends readily to characteristic polynomials,
since they are defined as determinants. More precisely, let us 
consider the function $\chi : M_n(K) \to K_n[X]$ taking a matrix 
$M$ to its monic characteristic polynomial $\det(X-M)$.
Then $\chi$ is differentiable at each point $M \in M_n(K)$ and its 
differential is given by $dM \mapsto \tr(\com(X{-}M) \cdot dM)$.
